### 2015-11-24 ch02-qlogms/excitation-design.tex
Some updates to CH02

  \begin{property}
   Each frequency band $B = \ClosedInterval{f, \kappa f}$ with $\kappa \in \PositiveRealNumbers \without \set{0,1}$ that is completely within the range of the excited logarithmic grid of frequencies $\set{f_1, \ldots, f_F}$ contains a constant number of frequency lines
   \begin{equation}
     F_{B}(f) \isdef
     \floor{\frac{\log (\kappa f) - \log( f )}{\log \alpha}}
         = \floor{\log_{\alpha} \kappa}
         \text{.}
   \end{equation}
   \end{property}
  \begin{example}
    For the frequency decade band $\decade(f) \isdef \ClosedInterval{f, 10 f}$, a logarithmic frequency grid contains $F_{\decade} = \floor{\log_{\alpha} 10}$ excited lines.
  \end{example}
  \begin{example}
    The~\citep{HP3562A} has a logarithmic measurement mode that ensures that each decade is covered by $F_{\decade} = 80$ lines~ to measure an \gls{FRF}.
    This is equivalent to a grid spacing $\alpha = \sqrt[80]{10} \approx 1.029$.
  \end{example}

@@

  \begin{remark}
  The use of different rounding strategies in \eqref{eq:excitation:qlog:roundAlpha}, allows for slightly different guarantees on the effective $\alpha_k$ attained by the grid.
  By denoting $\alpha_k^{\placeholder}$ as the effective frequency ratio for a rounding strategy $\placeholder$  in that equation, one can trivially see that the following relationships hold:
  \begin{equation}
  \alpha_k^{\floor{}} \leq \alpha \leq  \alpha_k^{\ceil{}}
  \qquad \text{and} \qquad
  \alpha_k^{\floor{}} \leq \alpha_k^{\round{}} \leq  \alpha_k^{\ceil{}}
  \qquad
  \forall k \in \set{1,\ldots,F}
  \text{.}
  \end{equation}
  \end{remark}

@@

  Using this extension, the frequency range covered by $f_k$ can then be calculated as
    \begin{align}
      \fMin{k} &= \mean{f_{k-1}}{f_k}\\
      \fMax{k} &= \mean{f_{k+1}}{f_k}
    \label{eq:fRange}
    \text{.}
    \end{align}
  This range can be seen as the power-spectral density counterpart of the discrete spectrum relation \eqref{eq:nearestLines}.
  Consequently,

@@

  \begin{lemma} \label{lem:exc:sysscaling}
  Consider the second-order systems $G(\omega; \wn)$ and $G(\omega; m\wn)$ with $m \in \RealNumbersWithoutZero$. 
  For a frequency grid $\infgrid{\omega}$ with infinite span, it can be shown that $G(\infgrid{\omega}; \wn) = G(m \infgrid{\omega}; m\wn)$.
  \end{lemma}
  \begin{proof}
  Pick any $\omega_{\star} \in \infgrid{\omega}$. The frequency $m\omega_{\star}$ is then by definition an element of the grid $m\infgrid{\omega}$.
  Substituting $\omega = \omega_{\star}$ and $\omega = m \omega_{\star}$  into  $G(\omega; \wn)$ and $G(m\omega; m\wn)$  respectively, directly yields
  \begin{equation}
    \frac{\dc}{- \omega_{\star}^2 \wn^{-2} + 2j\damping \omega_{\star} \wn^{-1} + 1} = 
    \frac{\dc}{- (m\omega_{\star})^2 (m\wn)^{-2} + 2j\damping (m\omega_{\star}) (m\wn)^{-1} + 1}
    \text{.}
  \end{equation}
  Since all the factors ``$m$'' cancel in the equation above, this proves the stated.
  \end{proof}

  \begin{theorem}
    Second-order  systems with equal damping $\damping$ and \gls{DC} gain $\dc$ but resonance frequencies that differ by a factor $\alpha^N$ with $N \in \IntegerNumbers$, share an identical `shape` of their \gls{FRF} at the lines of a logarithmically spaced frequency grid with infinite span and a frequency ratio $\alpha$.
    Or, formally: $G(\infgrid{\omega};\wn) = G(\infgrid{\omega}; \alpha^{N}\wn) \forall N \in \NaturalNumbers$.
  \end{theorem}
  \begin{proof}
    This is an immediate consequence from Lemma~\ref{lem:exc:sysscaling} for $m= \alpha^{N}$ and Remark~\ref{rem:exc:gridscaling}.
  \end{proof}

>>>>

  \begin{property}
   Each frequency band $B = \ClosedInterval{f, \kappa f}$ with $\kappa \in \PositiveRealNumbers \without \set{0,1}$ that is completely within the range of the excited logarithmic grid of frequencies $\set{f_1, \ldots, f_F}$ contains a constant number of frequency lines
   \begin{equation}
     F_{B} \isdef
     \floor{\frac{\log (\kappa f) - \log( f )}{\log \alpha}}
         = \floor{\log_{\alpha} \kappa}
         \text{.}
   \end{equation}
   \end{property}
  \begin{example}
    For the frequency decade band $\decade(f) \isdef \ClosedInterval{f, 10 f}$, a logarithmic frequency grid contains $F_{\decade} = \floor{\log_{\alpha} 10}$ excited lines.
  \end{example}
  \begin{example}
    The~\citep{HP3562A} has a logarithmic measurement mode that ensures that each decade is covered by $F_{\decade} = 80$ lines~ to measure an \gls{FRF}.
    This is equivalent to a grid spacing $\alpha = \sqrt[80]{10} \approx 1.029$.
  \end{example}

@@

  \begin{remark}
  The use of different rounding strategies --- e.g. the \code{ceil} function $\ceil{}$  and \code{floor} function $\floor{}$ --- in \eqref{eq:excitation:qlog:roundAlpha}, allows for slightly different guarantees on the effective $\alpha_k$ attained by the grid.
  By denoting $\alpha_k^{\placeholder}$ as the effective frequency ratio for a rounding strategy $\placeholder$  in that equation, one can trivially see that the following relationships hold:
  \begin{equation}
  \alpha_k^{\floor{}} \leq \alpha \leq  \alpha_k^{\ceil{}}
  \qquad \text{and} \qquad
  \alpha_k^{\floor{}} \leq \alpha_k^{\round{}} \leq  \alpha_k^{\ceil{}}
  \qquad
  \forall k \in \NaturalNumbersWithoutZero
  \text{.}
  \end{equation}
  This means that rounding using the \code{floor} operator favors to strictly attain the specified frequency bin density at the cost of a few more excited lines (and hence less allottable power per line).
  The \code{ceil} function produces a grid that has more power per line at the cost of a reduced bin density.
  On the other hand, using \code{round} as in \eqref{eq:excitation:qlog:roundAlpha}, provides a grid that is somewhere in-between both extremes.
  \end{remark}

@@

  Using this extension, the frequency range covered by $f_k$ can then be calculated as
    \begin{align}
      \fMin{k} &= \mean{f_{k-1}}{f_k}\\
      \fMax{k} &= \mean{f_{k+1}}{f_k}
    \label{eq:fRange}
    \text{.}
    \end{align}
  This range can be seen as the power-spectral density counterpart of the discrete spectrum relation \eqref{eq:nearestLines}.
  Consequently, both signals can be expected to behave in approximately the same way.

@@

  \begin{lemma} \label{lem:exc:sysscaling}
  Consider the second-order systems $G(\omega; \wn)$ and $G(\omega; m\wn)$ with $m \in \RealNumbersWithoutZero$. 
  For a frequency grid $\infgrid{\omega}$ with infinite span, $G(\infgrid{\omega}; \wn) = G(m \infgrid{\omega}; m\wn)$.
  \end{lemma}
  \begin{proof}
  Consider any $\omega_{\star} \in \infgrid{\omega}$. The frequency $m\omega_{\star}$ is then by definition an element of the grid $m\infgrid{\omega}$.
  Substituting $\omega = \omega_{\star}$ and $\omega = m \omega_{\star}$  into  $G(\omega; \wn)$ and $G(m\omega; m\wn)$  respectively, directly yields
  \begin{equation}
    \frac{\dc}{- \omega_{\star}^2 \wn^{-2} + 2j\damping \omega_{\star} \wn^{-1} + 1} = 
    \frac{\dc}{- (m\omega_{\star})^2 (m\wn)^{-2} + 2j\damping (m\omega_{\star}) (m\wn)^{-1} + 1}
    \text{.}
  \end{equation}
  Since all the factors ``$m$'' cancel in the equation above, this proves the stated.
  \end{proof}

  \begin{theorem}
    Second-order  systems with equal damping $\damping$ and \gls{DC} gain $\dc$ but resonance frequencies that differ by a factor $\alpha^N$ with $N \in \IntegerNumbers$, share an identical `shape` of their \gls{FRF} at the lines of a logarithmically spaced frequency grid with infinite span and a frequency ratio $\alpha$.
    Or, formally: $\forall N \in \NaturalNumbers: G(\infgrid{\omega};\wn) = G(\infgrid{\omega}; \alpha^{N}\wn)$.
  \end{theorem}
  \begin{proof}
    This is an immediate consequence from Lemma~\ref{lem:exc:sysscaling} for $m= \alpha^{N}$ and Remark~\ref{rem:exc:gridscaling}.
  \end{proof}
